Real Estate

### 2022-10-28 src/real_estate.Rmd
normalized data

```{r}
# aggregate yardi data into MSAs by cbsa
MSA_realEstate_data <- city_realEstate_data %>%

@@

```{r}
# calculate rent to income ratio

# YoY rent change
```

@@

```{r}

```{r}
# normalize everything into new data table

normalized <-

>>>>

```{r}
# select columns in demographic data
MSA_demo_data <- MSA_demo_data %>% 
  clean_names() %>% 
    # calculate income to home price
  mutate(income_to_homeprice = median_income_usd_2021/house_price_2021) %>% 
  select(cbsa, msa, state, employment_yo_y21_22, pop_percent_change20_21, median_income_usd_2021, income_to_homeprice)
```

```{r}
# aggregate yardi data into MSAs by cbsa
MSA_realEstate_data <- city_realEstate_data %>% 
  clean_names() %>% 
  group_by(cbsa) %>% 
  # calculate average values for MSAs with more than one city
  summarize(avg_rent_2021 = mean(average_rent_2021, na.rm = TRUE),
            avg_rent_2022 = mean(x2022_rent, na.rm = TRUE),
            avg_occupancy_21 = mean(percent_occupancy_2021, na.rm = TRUE)) %>% 
  # calculate change in rent
  mutate(rent_change21_22 = (avg_rent_2022- avg_rent_2021)/avg_rent_2021)

@@

```{r}
# combine real estate and demographic data by cbsa
MSA_realEstate_data <- MSA_demo_data %>% 
  left_join(MSA_realEstate_data) %>% 
  # calculate rent to income ratio
  mutate(rent_to_income = avg_rent_2021/median_income_usd_2021)

```{r}
```

@@

```{r}
# normalize columns into new data table
n_MSA_realEstate_data <- MSA_realEstate_data %>% 
  # normalize population data
  mutate(n_pop_change = (pop_percent_change20_21 - min(pop_percent_change20_21))/(max(pop_percent_change20_21)-min(pop_percent_change20_21))) %>% 
  # normalize employment growth
  mutate(n_employ_change = (employment_yo_y21_22 - min(employment_yo_y21_22)) / (max(employment_yo_y21_22) - min(employment_yo_y21_22))) %>% 
  # normalize rent to income
  mutate(n_rent_to_income = (rent_to_income- min(rent_to_income)) / (max(rent_to_income) - min(rent_to_income))) %>% 
  # normalize income to home price
  mutate(n_income_to_homeprice = (income_to_homeprice - min(income_to_homeprice)) / (max(income_to_homeprice) - min(income_to_homeprice)))
